\section{Notation}\label{sec:notation}

\subsection{Sets and Numbers}

\begin{itemize}
  \item $\NN$ denotes the set of natural numbers $\{0, 1, 2, \ldots\}$.
  \item $\ZZ$ denotes the set of integers.
  \item $\ZZ_p$ denotes the set of integers modulo $p$, i.e., $\{0, 1, \ldots, p-1\}$.
  \item $\ZZ_p^*$ denotes the set of integers modulo $p$ excluding zero, i.e., $\{1, 2, \ldots, p-1\}$.
  \item $[n]$ denotes the set $\{1, 2, \ldots, n\}$ for a positive integer $n$.
  \item $[a, b]$ denotes the set $\{a, a+1, \ldots, b\}$ for integers $a \leq b$.
  \item $\{0, 1\}^n$ denotes the set of all binary strings of length $n$.
  \item $\{0, 1\}^*$ denotes the set of all binary strings of finite length.
\end{itemize}

\subsection{Probability and Sampling}

\begin{itemize}
  \item $x \sample S$ denotes sampling $x$ uniformly at random from the finite set $S$.
  \item $x \gets \algo{A}(y)$ denotes running algorithm $\algo{A}$ on input $y$ and assigning the output to $x$.
  \item $\Pr[E]$ denotes the probability of event $E$.
  \item $\defeq$ denotes a definition, i.e., the left side is defined to equal the right side.
\end{itemize}

\subsection{Cryptographic Notation}

\begin{itemize}
  \item $\secpar$ denotes the security parameter.
  \item $\secparam$ denotes the security parameter in unary representation.
  \item $\negl$ denotes a negligible function in the security parameter.
  \item \ppt stands for probabilistic polynomial-time.
\end{itemize}

\subsection{Groups and Fields}

\begin{itemize}
  \item $\gparam$ denotes group parameters, where $\GG$ denotes a cyclic group, $g$ denotes the generator and $p$ denotes the order of a group.
  \item $1_\GG$ denotes the identity element of group $\GG$.
\end{itemize}

\subsection{Logical Operators}

\begin{itemize}
  \item $\wedge$ denotes logical AND.
  \item $\vee$ denotes logical OR.
  \item $\neg$ denotes logical NOT.
  \item $\oplus$ denotes bitwise XOR.
\end{itemize}

\subsection{Other Notation}

\begin{itemize}
  \item $\|$ denotes concatenation (e.g., $x \| y$ is the concatenation of $x$ and $y$).
  \item $|S|$ denotes the cardinality (size) of set $S$.
  \item $\bot$ denotes an error or undefined value.
  \item $\emptyset$ denotes the empty set.
  \item $\log_g(h)$ denotes the discrete logarithm of $h$ with respect to base $g$.
  \item $O(\cdot)$ denotes asymptotic upper bound (big-O notation).
\end{itemize}
